xwMOOC 딥러닝

### 2018-03-01 r-keras-cats-and-dogs.Rmd
compile...

car_airplane_model %>%
    layer_dense(units = 256, activation = 'relu', input_shape = c(2352)) %>%
    layer_dense(units = 128, activation = 'relu') %>%
    layer_dense(units = 2, activation = 'softmax')

@@

``` {r airplane-car-image-error}
## 3.5. 딥러닝 결과 보고서 작성
error_img_v <- car_airplane_df %>% filter(error == "bad") %>% 
    pull(img_no)

>>>>

car_airplane_model %>%
    layer_dense(units = 256, activation = 'relu', input_shape = c(2352)) %>%
    layer_dense(units = 128, activation = 'relu') %>%
    layer_dense(units = 64, activation = 'relu') %>%
    layer_dense(units = 2, activation = 'softmax')

@@

``` {r airplane-car-image-error, eval=FALSE}
## 3.5. 딥러닝 결과 보고서 작성
error_img_v <- car_airplane_df %>% filter(error == "bad") %>% 
    pull(img_no)
